Generating Interactive WebSocket Applications in TypeScript

### 2020-03-09 PLACES_2020/encoding.tex
PLACES: update receive transition explanation

\subparagraph{Receiving}
The payload of a message receive transition is passed as
a prop to the successor state and can be handled in the successor's view
function.
Upon a message receive event, the session runtime renders the
successor of the receive state and propagates the payload to the successor
accordingly.

>>>>

\subparagraph{Receiving}
The React component for a receiving state is required to
define a handler for each supported branch. 
Upon a message receive event, the session runtime invokes the
handler of the corresponding branch with the message payload and 
renders the successor state upon completion.
